My English activity log

### 2020-03-30 _posts/2019-11-04-my-english-activity-log/my-english-activity-log.Rmd
jusqu'au 30/03

author:
  - name: Aurélie Pinchart
date: 03-13-2020
preview: english.jpg
output:
  distill::distill_article:
    self_contained: false
---

@@

>>>>

author:
  - name: Aurélie Pinchart
date: 03-30-2020
preview: english.jpg
output:
  distill::distill_article:
    self_contained: false
---

@@

* **19/03/2020** : I watched a video about the immune system https://www.youtube.com/watch?v=fSEFXl2XQpc.

* **21/03/2020** : I watched a video about the endocrine system (part 1) https://www.youtube.com/watch?v=-pJOnYvKC4U.

* **27/03/2020** : I watched the second part of the video https://www.youtube.com/watch?v=LfqoRc68V5Q.

* **28/03/2020** : I watched "The Lord Of The Rings : The Fellowship Of The Ring" (long version, of course).

* **29/03/2020** : I watched "The Lord Of The Rings : The Two Tours".
